Analyzing the impact of social attributes on commit integration success

### 2017-02-20 Paper/MSRChallenge2017.tex
finished revisions to the conclusion

\section{Conclusion}
In this study we have analyzed the probability of Travis job success as being predicted by two different categories of attributes: Technical and Social data.
We gathered the attributes that describe complexity of each commit being pushed and have created a decision tree that predicts if a future pushed commit will be successfully integrated into its corresponding build or not.
Afterwards, we have gathered social attributes from the developers who pushed each of these commits
and we have augmented our dataset with these attributes to understand whether adding social information about the developer would help the decision tree predict with higher accuracy future 
instances.

Our results show that adding social data to the construction of the decision 
tree increases the probability this correctly predicting future commit's success 
in integrating into their corresponding projects by a margin of 4.09\% to 
11.99\%, depending on the ratio of successful vs unsuccessful instances are 
used to train the decision tree.

We have also found that non-core contributors cause not successful builds more
than core contributors.  This leads us to believe that non-core contributions
are not inspected as closely as they should be.  We have also found that having
a follower, and especially a large follower base, can be an indicator of build
integration success.

>>>>

\section{Conclusion}
In this study we have analyzed how technical and social factors can be used to
predict high quality contributions.  We have found that these factors provide
insight when predicting the success of a build with a technical factors leading
to a 14\% increase in predictive power, and another 12\% increase when
incorporating social factors into the prediction.

We have also found that being a core contributor and having a large follower
base can be an indicator of build integration success.
These results provide evidence that more experienced
developers are more likely to generate a high quality contribution.
